Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-03 paper/paper.qmd
Added link to shiny app in paper and readme.md

The dataset we used for this paper comes from The Washington's Post's GitHub repository, "How The Post mapped unsolved murders", which is also known as the "Unsolved Homicide Database" [@datahomicides]. We used the statistical programming language R [@citeR], tidyverse [@citetidyverse], janitor [@citejanitor], lubridate [@citelubridate], dplyr [@citedplyr], ggplot2 [@citeggplot2], arrow [@citearrow], testthat [@citetestthat], and knitr [@citeknitr] to retrieve, clean, test, and analyze the dataset. To construct, test, and analyze our model, we used the following packages: rstanarm [@citerstanarm], modelsummary [@citemodelsummary], and car [@citecar]. The causal model diagram created to understand the relationship between predictor variables, the outcome variable, and a confounder used DiagrammeR [@citeDiagrammeR], rsvg [@citersvg], DiagrammeRsvg [@citeDiagrammeRsvg] and png [@citepng]. To style our scripts, we used lintr [@citelintr] and styler [@citestyler].

@@

@@

## Code styling

>>>>

The dataset we used for this paper comes from The Washington's Post's GitHub repository, "How The Post mapped unsolved murders", which is also known as the "Unsolved Homicide Database" [@datahomicides]. We used the statistical programming language R [@citeR], tidyverse [@citetidyverse], janitor [@citejanitor], lubridate [@citelubridate], dplyr [@citedplyr], ggplot2 [@citeggplot2], arrow [@citearrow], testthat [@citetestthat], and knitr [@citeknitr] to retrieve, clean, test, and analyze the dataset. To construct, test, and analyze our model, we used the following packages: rstanarm [@citerstanarm], modelsummary [@citemodelsummary], and car [@citecar]. The causal model diagram created to understand the relationship between predictor variables, the outcome variable, and a confounder used DiagrammeR [@citeDiagrammeR], rsvg [@citersvg], DiagrammeRsvg [@citeDiagrammeRsvg] and png [@citepng].

@@

## Dashboard for Interactive Visualizations

A dashboard containing interactive versions of the graphs found in this paper was developed using shiny [@citeshiny], shinydashboard [@citeshinydashboard], and plotly [@citeplotly]. The link to the Shiny app can be found here: https://49z7k8-emily-su.shinyapps.io/unsolved-homicides-app/

@@

## Note on Code styling
